Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-05 WSSSPE3/report/wg_appendix_publishing_SW.tex
Section 5.9 and Appendix K: small changes.

\begin{itemize}
\item Steven R. Brandt -- Louisiana State University
\item Daniel Gunter -- LBNL
\item Yuhan Ding -- Illinois Institute of Technology
\item Neil Chue Hong -- Software Sustainability Institute
\end{itemize}

@@

\item ACM Transactions on Mathematical Software (TOMS): provides the extra step
of having reviewers validate the code which was submitted with the publication.

@@

\item Nature: offering a list of notebooks published alongside more traditional
articles, and is looking at ways to make these documents more official. There
are, in fact, a number of journals that offer ``electronic supplements'' to the
more traditionally published static articles.

@@

\item KBase: narratives build on IPython\slash Jupyter notebooks to build
publications that are reproducible, and can be commented or annotated.

@@

Create the first version of the web page to be displayed on the Software
Sustainability Institute's website: \url{http://www.software.ac.uk}.
We expect the page to be live in early January of 2016.

@@

Steven R.\ Brandt has created a first version of the page, and it is in the process
of being posted on the Software
Sustainability Institute's website: \url{http://www.software.ac.uk}. 
Neil Chue Hong will take responsibility for the page once it is up.

>>>>

\begin{itemize}
\item Steven R.\ Brandt -- Louisiana State University
\item Daniel Gunter -- LBNL
\item Yuhan Ding -- Illinois Institute of Technology
\item Neil Chue Hong -- Software Sustainability Institute
\end{itemize}

@@

\item ACM Transactions on Mathematical Software (TOMS): provides the additional step
of having reviewers validate the code which was submitted with the publication.

@@

\item Nature: offers a list of notebooks published alongside more traditional
articles, and is looking at ways to make these documents more official. There
are, in fact, a number of journals that offer ``electronic supplements'' to the
more traditionally published static articles.

@@

\item KBase: offers narratives built on IPython or Jupyter notebooks for assembling
publications that are reproducible, and can be commented or annotated.

@@

Create the first version of the web page to be displayed on the Software
Sustainability Institute's website. %: \url{http://www.software.ac.uk}. \choinote{already appeared above)
We expect the page to be live in early January of 2016.

@@

Steven R.\ Brandt has created a first version of the page, and it is in the process
of being posted on the Software
Sustainability Institute's website. %: \url{http://www.software.ac.uk}.  \choinote{already appeared above)
Neil Chue Hong will take responsibility for the page once it is up.

### 2016-02-05 WSSSPE3/report/wg_main_publishing_SW.tex
Section 5.9 and Appendix K: small changes.

This group explored the value of executable papers (papers whose content
includes the code needed to produce their own results), and other forms of
publishing which include dynamic electronic content.
%
%\subsubsection{Why it is important}
%
Transitioning to this type of publication offers possibilities of addressing, or
partially addressing, sustainability concerns such as reproducibility, software
credit, and best practices.

@@

\textbf{Software Credit (\S\ref{sec:software-credit})}: Since these forms of
publishing must make their sources explicit in order to execute, they should be
easier to trace even if appropriately worded credit for software is not
provided. In addition, these notebooks make it possible to provide/define
additional metadata to make the tracing of credit clearer. Finally, attributions
could be added to citations to identify whether a paper extends a result,
verifies it, contradicts it, etc.

@@

The group felt that the best way to encourage the use of these new publishing
concepts would be to create and curate a list identifying publishing venues that
support them. The Software Sustainability Institute agreed to host this list.

>>>>

This working group explored the value of executable papers (papers whose content
includes the code needed to produce their own results), and other forms of
publishing which include dynamic electronic content.
%
%\subsubsection{Why it is important}
%
Transitioning to this type of publication offers possibilities of addressing, or
partially addressing, sustainability concerns such as reproducibility, software
credit, and best practices.

@@

\textbf{Software Credit (\S\ref{sec:software-credit})}: Since these forms of
publishing must make their sources explicit in order to execute, they should be
easier to trace even if appropriately worded credit for software is not
provided. In addition, some software notebooks (i.e., active or executable papers; 
see Appendix~\ref{sec:appendix_publishing_SW} for examples) 
make it possible to provide or define
additional metadata to make the tracing of credit clearer. Finally, attributions
could be added to citations to identify whether a paper extends a result,
verifies it, contradicts it, etc.

@@

The group felt that the best way to encourage the use of these new publishing
concepts would be to create and curate a list of publishing venues that
support them. The Software Sustainability Institute agreed to host this list.
